---
title: "gpelose_OriginalHomeworkCode_04"
author: "Greg Pelose"
date: "11/5/2019"
output: html_document
---

Question:

[1] Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).
***
First I need to dowload the KamilarAndCooperData.csv data. 
```{r}
install.packages("curl")
```

```{r}
library("curl")
```

```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

```{r}
m <- lm(log(HomeRange_km2) ~ log(Body_mass_female_mean), data = d)
m
```

I got -9.441 and 1.036 as my slope and my y-intercept. 

***
[2] Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β coefficient.
***
```{r}
logit.bootstrap <- function(data, indices) {

  d <- data[indices, ]
  fit <- lm(data = d, log(HomeRange_km2) ~ log(Body_mass_female_mean))

  return(coef(fit))
} #This function calculated the linear model for each output. 

set.seed(250) # random # generator

results <- boot(data=d, statistic=logit.bootstrap, R=1000) # 1000 samples 
results
```
You can see my standard error numbers with the results.


#everything below is me trying to figure this out.(ignore) I want to keep so I can see where I went wrong.
***
```{r}
install.packages("boot")
```
```{r}
library("boot")
```


```{r}
boot(data = f, statistics= m, R = 1000) 
```

```{r}
# function to obtain regression weights 
bs <- function(formula, data, indices) {
  d <- f[indices,] # allows boot to select sample 
  fit <- lm(log(HomeRange_km2) ~ log(Body_mass_female_mean), data=d)
  return(coef(fit)) 
} 
set.seed(800)

results <- boot(data, statistic=bs, R=1000)

```

```{r}
logit.bootstrap <- function(data, indices) {

  d <- data[indices, ]
  fit <- lm(data = d, log(h)~log(m))

  return(coef(fit))
} 

set.seed(200) 

results <- boot(data=d, statistic=logit.bootstrap, R=1000) # 1000 samples 
```

```{r}
set <- NULL 
n <- 15
for (i in 1:1000){
    set[i] <- mean(sample(f, n, replace=TRUE))
}
quantile(set, c(0.050, 0.950))
se(set)
```
***

Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap and determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution.

```{r}
boot.ci(results)
```

Everything below this was me trying to figure this out, dont, I am keeping it so i can see where I went wrong
***
```{r}
install.packages("sciplot")
```
```{r}
library("sciplot")
```
```{r}
se(set)
```

```{r}
upper <- mean(set) + qnorm(0.950, mean=0, sd=1)*se(set)
lower <- mean(set) + qnorm(0.050, mean=0, sd=1)*se(set) 
ci <- c(lower,upper)
ci
```
***

How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?

How does the latter compare to the 95% CI estimated from your entire dataset?



5 Problems with my code
1. I struggled to understand how to describe my data at the end of problem 2 in the homwork set. 
2. I made many mistakes attempting to try and figure out the second question of the homework problem, but after a while I think that I was able to figure it out.
3. I struggled to stay focused during this homework set, when I couldnt figure something out I started to lose focus.
4.I could not figure out the bootstrapping from the modules, I had to go look online to try and figure something out. I feel like I missed where the informationw as on how to bootstrap with linear regressions was on the modules.
5.I still feel jumbled up and messy with my annotations, what can I imporve on to make everything look better and more organized. 






