---
title: "gpelose_OriginalHomeworkCode_04"
author: "Greg Pelose"
date: "11/5/2019"
output: html_document
---

Question:

[1] Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).
***
First I need to dowload the KamilarAndCooperData.csv data. 
```{r}
install.packages("curl")
```

```{r}
library("curl")
```

```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

```{r}
m <- lm(log(HomeRange_km2) ~ log(Body_mass_female_mean), data = d)
m
```

I got -9.441 and 1.036 as my slope and my y-intercept. 

[2] Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β coefficient.
use package simple boot ot \\r boot

Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap and determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution.

How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?

How does the latter compare to the 95% CI estimated from your entire dataset?